---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `{packagename}`

<!-- badges: start -->
[![R-CMD-check](https://github.com/UCD-SERG/packagename/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UCD-SERG/packagename/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/UCD-SERG/packagename/graph/badge.svg)](https://app.codecov.io/gh/UCD-SERG/packagename)
[![CodeFactor](https://www.codefactor.io/repository/github/ucd-serg/packagename/badge)](https://www.codefactor.io/repository/github/ucd-serg/packagename)
[![CRAN status](https://www.r-pkg.org/badges/version/packagename)](https://CRAN.R-project.org/package=packagename)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{packagename}` is to ...

## Installation

You can install the development version of `{packagename}` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("UCD-SERG/packagename")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(packagename)
## basic example code
```

## Code of Conduct

Please note that the `{packagename}` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
